%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jaewon Bae} \\ \vspace{1pt}
    \small Toronto, ON $|$ 647-458-9968 $|$ \href{mailto:jaey.pro@gmail.com}{\underline{jaey.pro@gmail.com}} $|$ 
    \href{https://linkedin.com/in/jae-bae}{\underline{linkedin.com/in/jae-bae}} $|$
    \href{https://github.com/binding1}{\underline{github.com/binding1}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lighthouse Labs}{Toronto, ON}
      {Diploma in Web Development}{Oct. 2022 -- May 2023}
    \resumeSubheading
      {University of Ottawa}{Ottawa, ON}
      {Bachelors of Applied Sciences in Civil Engineering $|$ GPA: 3.70}{Sep. 2016 -- Jun. 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Junior Solutions Specialist}{Nov. 2022 -- Apr. 2023}
      {Method:CRM}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Acted as Consultant for 50+ small and medium-sized businesses using Method’s no-code CRM platform to tailor to unique business needs}
        \resumeItem{Compiled and document various client requirements in iterations which were translated into technical requirements, designs, and workflows}
        \resumeItem{Developed, tested, and delivered complex, custom SaaS solutions using programming logic and SQL queries}
        \resumeItem{Gathered continuous feedback, and translate into feature requests and support cases for product team in JIRA}
        \resumeItem{Integrated third-party software into in-house API to fetch and submit data into Method's back-end}
    \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Building Science Consultant}{May 2022 -- Nov. 2022}
      {WSP in Canada}{Thornhill, ON}
      \resumeItemListStart
        \resumeItem{Oversaw numerous construction projects and building condition assessments, through client meetings, repair methods and payment certifications}
        \resumeItem{Performed site reviews with field crew to monitor project progress and ensure conformance with schedule, specifications, and budget}
        \resumeItem{Collaborated with engineers and clients for engineering and management inquiries}
      \resumeItemListEnd

    \resumeSubheading
      {Project Coordinator}{Jun. 2021 -- Apr. 2022}
      {EllisDon}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Coordinated with project managers and contractors for various \$1M+ public projects throughout extensive project lifecycle phases}
        \resumeItem{Controlled project documents, Requests For Information and Change Orders and delegated tasks to proper contractor}
        \resumeItem{Assisted in procurement by producing scopes of work from design documents and performing analysis to award in the bidding process}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\href{https://github.com/binding1/budget-boss}{\textbf{\underline{BudgetBoss}}} $|$ \emph{Next.js, React.js, Prisma, Tailwind, Axios, Chart.js}}{May 2023 -- May 2023}
          \resumeItemListStart
            \resumeItem{Developed a full-stack single-page application using with Next.js serving REST API with React as the front-end}
            \resumeItem{Implemented Chart.js to visualize transaction data queried from Prisma into charts}
            \resumeItem{Used Tailwind for styling a clean and concise design}
          \resumeItemListEnd
      \resumeProjectHeading
          {\href{https://github.com/binding1/scheduler}{\textbf{\underline{Scheduler}}} $|$ \emph{React.js, SASS, Axios, Jest, Storybook, Cypress}}{Mar. 2023 -- Apr. 2023}
          \resumeItemListStart
            \resumeItem{Developed a single-page application for students to schedule interviews with mentors, front-end built with React}
            \resumeItem{Connected to API to fetch interview data}
            \resumeItem{Created functional components and custom hooks to implement DRY principles and state management}
          \resumeItemListEnd
                \resumeProjectHeading
          {\href{https://github.com/binding1/PasswordKeepR}{\textbf{\underline{PasswordKeepR}}} $|$ \emph{Embedded JavaScript, Express.js, SASS, Node.js, jQuery, PostgreSQL}}{Feb. 2023 -- Feb. 2023}
          \resumeItemListStart
            \resumeItem{Developed a multi-page web application made in collaboration in a team for managing passwords}
            \resumeItem{Wrote API handler for CRUD operations to save, edit and delete passwords}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Python, SQL (Postgres), Ruby, VBA, C} \\
     \textbf{Frameworks}{: React.js, Node.js, Next.js, HTML/CSS, SCSS, Prisma, Ruby on Rails, Tailwind, Express.js, Axios, jQuery} \\
     \textbf{Developer Tools}{: Git, GitHub, VS Code} \\
     \textbf{Libraries}{: Chart.js, Jest, Storybook, Cypress, Mocha, Chai} \\
     \textbf{Other}{: Agile, Project Management, Microsoft Office Suite, CAD, MATLAB}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
